The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
with line breaks

The theory presented here may be extended in several ways. 
- detailed comparison to specific experimental apparatus. will gle dynamics be visible? 
- the vertical dimension is incompletely modeled - stratification, etc
- explore saturation property dependence of system on rotation profile 
- different field geometries (e.g. radially varying)
- other radial boundary conditions
- drop axisymmetry
- comparison to simulation in both weakly and strongly nonlinear regimes

>>>>

The theory presented here may be extended in several ways. \\
- detailed comparison to specific experimental apparatus. will gle dynamics be visible? \\
- the vertical dimension is incompletely modeled - stratification, etc\\
- explore saturation property dependence of system on rotation profile\\ 
- different field geometries (e.g. radially varying)\\
- other radial boundary conditions\\
- drop axisymmetry\\
- comparison to simulation in both weakly and strongly nonlinear regimes\\
